\textbf{ Interpretable Gaussian Processes for Stellar Variability\\ I: Static Surfaces }

### 2020-12-14 tex/gitlinks.tex
more unit tests, fixed eqn typos

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/67220db9d930909e1b8a98ef092fc7b13860bd54/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/67220db9d930909e1b8a98ef092fc7b13860bd54/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/67220db9d930909e1b8a98ef092fc7b13860bd54/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/ccd46f868c6bcdeb26f56055d8dc023476fcd21b/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/ccd46f868c6bcdeb26f56055d8dc023476fcd21b/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/ccd46f868c6bcdeb26f56055d8dc023476fcd21b/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
